Project Report\\\textsc{DEVS Ex Machina}

### 2015-05-18 manual/projectrapport.tex
projectrapport changes

\chapter{Non-functional requirements}
\section{Correctness}
\subsubsection{Testing}
The use of the jenkins CI was heavily leveraged, in combination with extensive testing. Any feauture increment could only be merged into the project if it passed the developer's own jenkins instance.
\subsubsection{Thread races and deadlock}
Deadlocks and race conditions are very hard to debug, let alone prevent. To help us in this area as much as possible we used prototypes of threaded code in the tests before merging them into the main classes, and each build is checked with ThreadSanitizer \cite{tsan} which proved invaluable in preventing races and deadlocks in the threaded codepaths.
\subsubsection{Memory leaks and undefined behaviour}
With most entities represented as smart pointer, the need to ensure a leak free simulator nevertheless remained. To check for allocation misuse and a whole other series of errors we used Valgrind \cite{vg}. This meant for example that we detected a leak caused by circular referencing smart pointers.

@@

\section{Single core}

@@

\subsection{DirectConnect}

@@

\subsection{Dynamic Structured}

@@

\section{Further work.}
Further optimizations included but are not limited to: 
\begin{enumerate}
\item Custom memory allocators/pools (boost, ...)
\item Profiling guided recompilation
\item Detecting bottlenecks with perf and gprof.
\item ...
\end{enumerate}

>>>>

\chapter{Non-functional requirements}
\section{Correctness}
\subsubsection{Testing}
The use of the jenkins CI was heavily leveraged, in combination with extensive testing. Any feature increment could only be merged into the project if it passed the developer's own jenkins instance.
\subsubsection{Thread races and deadlock}
Deadlocks and race conditions are very hard to debug, let alone prevent. To help us in this area as much as possible we used prototypes of threaded code in the tests before merging them into the main classes, and each build is checked with ThreadSanitizer \cite{tsan} which proved invaluable in preventing races and deadlocks in the threaded codepaths.
\subsubsection{Memory leaks and undefined behaviour}
With most entities represented as smart pointer, the need to ensure a leak free simulator nevertheless remained. To check for allocation misuse and a whole other series of errors we used Valgrind \cite{vg}. This meant for example that we detected a leak caused by circular referencing smart pointers.

@@

\subsection{Single core}

@@

\subsubsection{DirectConnect}

@@

\subsubsection{Dynamic Structured}

@@
